The pollination trade-off

### 2019-04-09 paper/manuscript.Rmd
Load msc data in its own chunk so that the drake dependences are correctly calculated

@@

**Keywords:** X,Y,Z (up to 10)

**Type of article:** Letter

**Number of words:** `r readd(abs_wordcount)$n_words_stri` in the abstract; `r format(round(readd(msc_wordcount)$n_words_stri/10)*10, big.mark = ",")` in the main text.

**Number of displays:** `r readd(n_displays)$figures` figures; `r readd(n_displays)$tables` tables; `r readd(n_displays)$text_boxes` text boxes.

**Number of references:** `r readd(n_references)`

**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153)

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE, dpi = 300)

loadd(abs_cordcount, msc_wordcount, n_displays, n_references)
```

@@

**Keywords:** X,Y,Z (up to 10).

**Type of article:** Letter.

**Number of words:** `r abs_wordcount$n_words_stri` in the abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in the main text.

**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.

**Number of references:** `r n_references`

**Author for correspondence:** E. Fernando Cagua (+64 20 4026 8153).

@@
